\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-09-30 paper2015asml.tex

The library of trajectory videos was collected by computing plans with each of the previously discussed planners for the planning queries and scenes hand-picked from above. The plans were then recorded in simulation through RVIZ. In designing the online survey, these video recordings would be taken from multiple vantage points to maximize the visibility of the motion to the participant reviewing it.

@@

Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design. We ran the survey for 103 trajectories, requesting no more than 20 ratings per trajectory. Participants are allowed to rate multiple distinct trajectories, but no more than once.The analysis of these results will be done in Section~\ref{sec:analysis}.

>>>>

The infrastructure we designed around MoveIt! allowed us to automatically generate movies of the generated trajectories using the ROS Visualizer (Rviz). We generated movies from different viewpoints to maximize the visibility of the motion to human observers reviewing it. Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design. We ran the survey for 103 trajectories, requesting no more than 20 ratings per trajectory. Participants are allowed to rate multiple distinct trajectories, but no more than once. The analysis of these results is presented in Section~\ref{sec:analysis}.

@@
